### 2022-01-24 input/experiments.tex
miaw

\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that enables \emph{lazy}
    dynamic partitioning by allowing gateways to stop notifications
    when their respective network does not appear to have a source.

>>>>

\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the 2 additional pages available for the
    camera-ready version of the paper} dynamic partitioning by
    allowing gateways to stop notifications when their respective
    network does not appear to have a source.
